The ChEMBL database as Linked Open Data

### 2012-07-09 article.tex
Tuned up the abstract

\begin{abstract}
\paragraph*{Background:}
Making data available as Linked Data using RDF is advantageous because it promotes integration with other web resources.
RDF documents can natively link to related data, and others can link back using URIs. RDF makes the data machine-readable,
using extensible vocabularies for additional information. This combination provides a new, open, interface for scientists to use ChEMBL.
\paragraph*{Results:}
This paper describes the continued conversion of data from the ChEMBL database into RDF triples.
This updated version of ChEMBL-RDF now uses recently introduced ontologies, including CHEMINF and CiTO,
exposes more information from the database, and is now available as dereferencable, Linked Data.
To demonstrate the new features, we present new use cases showing the benefits of integration with
other web resources using semantic web technologies.
\paragraph*{Conclusions:}
\end{abstract}

>>>>

\begin{abstract}
\paragraph*{Background:}
Making data available as Linked Data using Resource Description Framework (RDF) promotes integration with other web resources.
RDF documents can natively link to related data, and others can link back using Universal Resource Identifiers (URIs).
RDF makes the data machine-readable, using extensible vocabularies for additional information, making it easier
to scale up inference and data analysis.
\paragraph*{Results:}
This paper describes the continued project to convert data from the ChEMBL database into RDF triples.
This updated version of ChEMBL-RDF now uses recently introduced ontologies, including CHEMINF and CiTO,
exposes more information from the database, and is now available as dereferencable, linked data.
To demonstrate these new features, we present novel use cases showing further integration with
other web resources, including Bio2RDF, Chem2Bio2RDF, and ChemSpider, and showing the use of standard
ontologies.
\paragraph*{Conclusions:}
The use cases show that by using open standards and ontologies it is possible to link the ChEMBL database
to other databases, such that the integration can understood by software. 
\end{abstract}
